### 2019-05-06 paper-one/paper-one.tex
paper four first post
notes recorded for paper four
registration info for paper one, makefile build

\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
     \Huge\textbf{Vipassana for Hackers}\\
     \vspace{5cm}
     \large\textit{Steven Deobald}\\
     \large\textit{Version 1.6}\\
     \large\textit\today\\
     \vspace{5cm}
     \large\textit{Contributions by: Preethi Govindarajan, Mat Kelly, Liam Monahan}\\
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}

@@

This paper will endeavour to avoid falling into the trap of ``Buddhist Guys'' (a mildly derogatory term coined by a serious meditator friend of mine). You might be familiar with phrases commonly attributed to this archetype such as ``When the student is ready, the teacher will appear.'' Mysticism, mystery, and mystique are to be avoided. If I fall into this trap, email me: \href{mailto:steven@nilenso.com}{steven@nilenso.com}

@@

Vipassana requires a 10-day course to learn. Anapana does not. Before his death, S.N. Goenka released both 70-minute audio instructions as MP3s for the Anapana meditation technique.\cite{anapana} The 70-minute instructions can be found at \url{http://www.vipassana.co/What-is-Anapana} under ``Anapana Meditation for All'' and come as four 15-minute sessions plus a 10-minute ``daily practice'' session.

\begin{figure}[H]
  \centering
  \includegraphics[width=8cm]{images/bridge.png}
  \label{fig:bridge}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/wall.jpg}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/bridge.png}
  \end{subfigure}
  \label{fig:wall}
\end{figure}

@@

@@

\bibitem{anapana}
  S.N. Goenka
  \url{http://www.vipassana.co/What-is-Anapana}
  \textit{What is Anapana?}
  Vipassana Research Institute, 21 October 2016.

@@

>>>>

\begin{titlepage}
   \vspace*{\stretch{1.0}}
   \begin{center}
     \Huge\textbf{Vipassana for Hackers}\\
     \Huge{Paper One: Curious Mechanics}\\
     \vspace{5cm}
     \large\textit{Steven Deobald}\\
     \large\textit{Version 1.6}\\
     \large\textit\today\\
     \vspace{5cm}
     \large\textit{Contributions by: Preethi Govindarajan, Mat Kelly, Liam Monahan}\\
   \end{center}
   \vspace*{\stretch{2.0}}
\end{titlepage}

@@

This paper will endeavour to avoid falling into the trap of ``Buddhist Guys'' (a mildly derogatory term coined by a serious meditator friend of mine). You might be familiar with phrases commonly attributed to this archetype such as ``When the student is ready, the teacher will appear.'' Mysticism, mystery, and mystique are to be avoided. If I fall into this trap, email me: \href{mailto:steven@deobald.ca}{steven@deobald.ca}

@@

Vipassana requires a 10-day course to learn. Anapana does not. Before his death,
S.N. Goenka released 70-minute audio instructions (for children) and 20-minute audio
instructions (for adults) as MP3s for the Anapana meditation technique.\cite{anapana}
Both 70-minute and 20-minute instructions can be found at
\url{https://www.vridhamma.org/what-is-anapana/} under ``Anapana Meditation for
All''. Under the videos are links to a 10-minute daily practice session, labelled
``Group Sitting'' under each respective language.

@@

@@

\begin{center}
  \Huge{Try it Yourself}
\end{center}

If you have not tried a 10-day Vipassana course, I have tried to repeatedly warn you
within the bounds of this paper that reading this paper doesn't really teach you
anything about Vipassana. The 10-day course serves two purposes: First, to try the
technique yourself to see if it suits you. Second, to learn how to meditate so you
can practice on your own. Both of these are possible only with direct experience. You
can't learn how to meditate by reading a paper like this. You have to try it.

If you would like to try it, Vipassana centres exist in many countries and the
instructions have been translated into most languages. You can apply for a course
near you online at \url{https://www.dhamma.org/en-US/courses/search} \cite{dhamma}.

\begin{center}
  \LARGE{A Word of Warning}
\end{center}

This paper exists solely to pique your interest in trying a serious meditation
practice yourself. Unfortunately, in detailing the mechanics of the technique, it is
likely to become a hindrance for some people. A reader of this paper may be tempted
to return to the contents of the paper for assistance during meditation. Please do
not do that. If you choose to take a 10-day Vipassana course, mentally set this paper
aside and follow the instructions given very carefully and attentively. The 10-day
course is very detailed and thoughtfully designed --- a very systematic way of
learning meditation in a relatively short period of time. This paper is only intended
to inspire you to try it.

@@

\bibitem{anapana}
  S.N. Goenka
  \url{https://www.vridhamma.org/what-is-anapana/}
  \url{https://www.vridhamma.org/Mini-Anapana-English}
  \textit{What is Anapana?}
  Vipassana Research Institute, 21 October 2016.

@@

\bibitem{dhamma}
  Vipassana International Academy
  \url{https://www.dhamma.org}
  \textit{Vipassana Meditation Website}
